%-------------------------
% Resume in Latex
% Author : Kaleab Alemayehu
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[a4paper, top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{latexsym}
% \usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
%-------------------------
% Resume in Latex
% Author : Kaleab Alemayehu
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kaleab Alemayehu} \\ \vspace{1pt}
    \small +251-942-323-094 $|$ \href{mailto:kaleabalemayehu04@gmail.com}{\underline{kaleabalemayehu04@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/kaleab-alemayehu-a3218422a/}{\underline{https://www.linkedin.com/in/kaleab-alemayehu-a3218422a/}} $|$
    \href{https://github.com/kaleabAlemayehu}{\underline{github.com/kaleabAlemayehu}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bahir Dar University}{Bahir Dar, Ethiopia}
      {Bachelor of Engineering in Software Engineering}{Jun. 2021 -- Jun 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Fullstack Developer}{Nov 2025 -- Present}
      {Alet-Systems ( MSA with Lakipay )}{Addis Ababa, Ethiopia}
      \resumeItemListStart
        \resumeItem{Implemented a robust RESTful API for a gifter mini app on Lakipay, enabling users to send gifts to influencers.}
        \resumeItem{Designed dynamic worker pools to consume webhook requests from Redis queues and batch database operations, preventing database overload.}
        \resumeItem{Developed a Golang SDK for seamless Lakipay integration.}
        \resumeItem{Built a real-time overlay system for OBS and TikTok Studio using WebSockets to display animated overlays when gifts are sent.}
        \resumeItem{Implemented an admin panel for the gifter mini app within the Lakipay Admin Panel using Next.js, ensuring a smooth administrative experience.}
      \resumeItemListEnd
      
      \resumeSubheading
        {Mid-Level Backend Developer}{Nov 2025 -- Present}
        {Awura Technologies}{Addis Ababa, Ethiopia}
        \resumeItemListStart
          \resumeItem{Implemented a RESTful API using state machines and event-driven architecture, publishing messages to RabbitMQ for user notifications.}
          \resumeItem{Designed a reliable and configurable cron job system with dynamic worker pools to process background tasks and perform batched database updates.}
          \resumeItem{Applied optimistic locking to maintain data consistency and prevent race conditions in concurrent operations.}
        \resumeItemListEnd
      \resumeSubheading
        {Fullstack Developer}{Jul 2024 -- Nov 2024}
        {Minab IT Solutions}{Addis Ababa, Ethiopia}
        \resumeItemListStart
          \resumeItem{Design and implement a robust web-based administration panel that Hahujobs CMS uses.}
          \resumeItem{Develop an SDK for ArifPay Integration using Golang.}
          \resumeItem{Integrate Arifpay into the Internal Product.}
        \resumeItemListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Backend Intern}{Jun 2024 - Sep 2024}
%     \resumeItemListStart
%        \resumeItem{Develop a Payroll Management System}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Backend Intern}{Jun 2024 - Sep 2024}
      {Kuraz Technologies}{Addis Ababa, Ethiopia}
      \resumeItemListStart
        \resumeItem{Develop a Payroll Management System}
        \resumeItem{Led a team of 6 interns in developing assigned projects under the guidance of an advisor, ensuring successful execution and collaboration throughout the process.}
    \resumeItemListEnd

    % \resumeSubheading
    %   {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
    %     \resumeItem{Developed a game in Java to test the generated dungeons}
    %     \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
    %     \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
    %     \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
    %     \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
       \resumeProjectHeading
         {\textbf{Payment Gateway Service} $|$ \emph{Golang, PostgreSQL, Docker, RabbitMQ, Echo}} {Dec 2025 -- Present}
         \resumeItemListStart
           \resumeItem{Built an idempotent payment service using Golang, PostgreSQL, and RabbitMQ.}
           \resumeItem{Developed RESTful APIs using Go’s \texttt{Echo} framework.}
           \resumeItem{Implemented the \texttt{Transactional Outbox Pattern} to handle dual-write consistency and ensure idempotent message publishing.}
           \resumeItem{Designed dynamic worker pools to process payments asynchronously and deliver results to client webhook endpoints.}
           \resumeItem{Applied row-level locking to ensure data consistency and prevent race conditions during concurrent transactions.}
           \resumeItem{Implemented retry queues and dead-letter queues to reliably handle failed payment events.}
           \resumeItem{Containerized the full development environment using Docker and Docker Compose for consistent and reproducible builds.}
        \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Drivee} $|$ \emph{Golang, Vue.js, PostgreSQL, Docker, Memcached, TailwindCSS}} {May 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Building a peer-to-peer car rental platform where users can list and rent vehicles.}
            \resumeItem{Developed the backend using Go's \texttt{net/http} for REST APIs.}
            \resumeItem{Created the frontend with Vue.js, using TailwindCSS, without any external UI libraries.}
            \resumeItem{Added Google and Twitter (X) SSO for login and user data access.}
            \resumeItem{Used Memcached to speed up response times by caching frequent API data.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Eagle Commerce} $|$ \emph{Golang, Go-Chi, NATS, MongoDB, Docker, Microservices, Hexagonal Architecture}} {Jul 2025 -- Jul 2025}
          \resumeItemListStart
            \resumeItem{Designed and developed a distributed e-commerce backend using Hexagonal Architecture. The system consisted of \texttt{order-ms}, \texttt{payment-ms}, \texttt{product-ms}, \texttt{user-ms}, and an \texttt{api-gateway}.}
            \resumeItem{Implemented RESTful APIs using \texttt{Go-Chi} across all services.}
            \resumeItem{Utilized \texttt{NATS} for asynchronous, event-driven communication between services.}
            \resumeItem{Built a robust API Gateway to proxy requests to services and enforce rate limiting.}
            \resumeItem{Leveraged MongoDB for efficient document-based data storage across services.}
          \resumeItemListEnd
          \resumeProjectHeading
            {\textbf{ Werewolf Game Bot } $|$ \emph{Go, PostgreSQL, Docker, Event-Driven Architecture, Pub/Sub}} {Aug 2025 -- Present}
            \resumeItemListStart
              \resumeItem{Engineered a feature-rich Telegram bot in Go, used by multiple active groups to play the game of Werewolf. The bot leverages a sophisticated state machine to manage the entire game lifecycle, including complex phases, roles, and player actions.}
              \resumeItem{Architected the application using Clean Architecture principles and a custom Pub/Sub event broker to create a decoupled, concurrent, and maintainable codebase.}
              \resumeItem{Authored a public blog post detailing the design and implementation of the event-driven model. \href{https://kaleabalemayehu.github.io/blog/pubsub/}{\underline{blog}.}
              \resumeItem{Drove a 4x reduction in hosting costs by analyzing performance and optimizing server resource allocation.}
              \resumeItem{Integrated PostgreSQL for persistent data storage, using goose for schema management and sqlc to generate type-safe Go code from raw SQL, improving reliability and developer productivity.}
              % \resumeItem{Containerized the complete development environment using Docker and Docker Compose to ensure consistent and reproducible builds.}
    \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Foodopia} $|$  \emph{Nuxt.js, Golang, PostgreSQL, Hasura, Apollo GraphQL, Docker, Flowbite}} {Jun 2024 -- Jul 2024}
          \resumeItemListStart
            \resumeItem{Built a recipe-sharing platform with user authentication, recipe creation, editing, filtering, and bookmarking.}
            \resumeItem{Used Hasura as the GraphQL engine and Gin (Go) for custom webhook handlers with a PostgreSQL database.}
            \resumeItem{Developed the frontend using Nuxt.js with Flowbite as the UI component library.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pong} $|$ \emph{Golang, Go-Raylib}} {Mar 2025 -- Mar 2025}
          \resumeItemListStart
            \resumeItem{Built a multiplayer Pong game over LAN.}
            \resumeItem{Developed the client side using Go-Raylib, a Go binding for the Raylib game library.}
            \resumeItem{Created the server side with Golang and handled game state synchronization using UDP.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Audiobook Downloader Bot} $|$ \emph{Grammy.js, TypeScript, JSDOM}} {Aug 2024}
          \resumeItemListStart
            \resumeItem{Built a Telegram bot that downloads audiobooks by scraping search results from the web.}
            \resumeItem{Implemented inline keyboard interactions using Grammy.js and TypeScript.}
            \resumeItem{Built a web scraper using JSDOM and the Fetch API to extract audiobook links from search results.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Typescript, Javascript, SQL (Postgres), Python, Lua, C/C++, HTML/CSS} \\
     \textbf{Frameworks}{: Vue, React, Nuxt, Next, Gin, Echo, Hugo, Node.js, TaiwlindCSS, headless-UI, Shadcn/ui, flowbite} \\
     \textbf{Developer Tools}{: Git, Docker, Neovim, Linux, Nix, VS Code} \\
     \textbf{Technologies}{: Kafka, NATS, RabbitMQ, GraphQL, PostgreSQL, SQLite, MongoDB, Redis, Memcached} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
